Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
added comments from Numair; added chi-squared test

% heather - add more results in here since we have more to report. Probably cut down image manipulation?
\begin{abstract}
We introduce Rewind system which assists in the recall of memory by automatically recreating interactive sceneries of past trips. Rewind system uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images. Since the effectiveness of memory cues is determined by their level of integration with the target memory, images used in Rewind system are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience. Users can interactively go back and forth in time by scrubbing over the video. Together, the composed video offer users a window into past travels. We report the results of a user study with eighteen participants conducted to collect location data over two weeks. Trips taken in groups were more likely to be recalled using Rewinds than trips taken alone. Rewind also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still preserve believable representations that capture the past.
\end{abstract}

\keywords{
Digital memories, geolocation, streetside images, travel.
}

@@

Geolocation data that can be automatically tracked and logged on a smartphone can be used to recreate context: to look up the weather at each moment, retrieve street side photos (e.g. from Google Street View) at every step, and compute the mode of transportation (e.g., \cite{zheng2008learning}) and nearby geographical features. The Rewind system takes those cues and manipulates the conditions of retrieved photos to re-imagine what a person saw at some past point in time. The sequences of visuals are stitched together into an interface that allows users to directly manipulate the point in time being shown by scrubbing back and forth (Figure~\ref{fig:scrubbing}). So all a person has to do is enable location tracking on their mobile device to later rewind and re-experience a past trip.

@@

\section{Related Work}
% heather - trips vs locations -> (define) semantic memory vs episodic memory - check references, relate to some work done by SenseCam perhaps?
% cut down GPS usage
\subsection{Digital Memories}
Rewind is guided by literature about mediated memories, which provides a theoretical underpinning behind how the Rewind experience is constructed. \textit{Mediated Memories in the Digital Age} offers inspiration informing the relationship between experiences and memories \cite{van2007mediated}. van Dijck notes, ``Remembering is vital to our well being, because without autobiographical memories we would have no sense of past or future, and we would lack any sense of continuity'' (pg. 3). Rewind aims to give the user this sense of continuity in a time segment which has a past and future. By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner. Similarly in his famous seminal paper \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through``associative trails'', giving mankind the ability of``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''. Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one’s sensory experiences about past visits.

@@

% heather - need to be rephrased perhaps? Should we give a high level summary of all the relationships we've found? More analysis to be done for photo vs. videos, another table?
% semantic vs episodic memory
% mention distance categories in the beginning (up up up) + everything else 
\section{Findings}
The findings of our user study center on the participants’ relationships to the Rewinds generated from their location data compared to the static photos. We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds. We also discuss the participants' interactions with and reactions to their Rewinds. The results use data from the user studies conducted with 12 men and 6 women. Half of the participants identified themselves as frequent travelers. Additionally, half of the participants were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them.

Our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media:
\begin{enumerate}
	\item Distance: how does the location's distance away from the participant's home influence the participant's perception of Rewinds and static photos? Distances ranged from 0 to 206,155 meters. For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 was 10--100 meters; Group 2 was 100--1,000 meters; Group 3 was 1,000--10,000 meters; Group 4 was 10,000--100,000 meters and Group 5 was 100,000--1,000,000 meters from the participant's home location.  
	\item Visit frequency: do participants react differently to Rewinds and static photos depicting locations they visit frequently compared to locations they rarely visit? We showed locations that were either ``most frequently visited,'' ``least frequently visited,'' or randomly selected.
	\item Companions: how does the presence of a traveling companion affect the participant's attitude toward Rewinds or static photos?
	\item Traveler type: do attitudes toward Rewinds and static photos differ depending on whether the participant identifies as a frequent traveler?
	\item GPS usage: do participants who are regular users of GPS navigation react differently to Rewinds and static photos compared to participants who don't use GPS navigation regularly?
\end{enumerate}

>>>>

% heather - add more results in here since we have more to report. Probably cut down image manipulation?
\begin{abstract}
We introduce the Rewind system which assists in the recall of memory by automatically recreating interactive sceneries of past trips. The Rewind system uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images. Since the effectiveness of memory cues is determined by their level of integration with the target memory, images used in Rewind system are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience. Users can interactively go back and forth in time by scrubbing over the video. Together, the composed video offer users a window into past travels. We report the results of a user study with eighteen participants conducted to collect location data over two weeks. Trips taken in groups were more likely to be recalled using Rewinds than trips taken alone. Rewind also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still preserve believable representations that capture the past.
\end{abstract}

% h - Numair suggested "recall" as another keyword
\keywords{
Digital memories, geolocation, streetside images, travel, recall.
}

@@

Geolocation data that can be automatically tracked and logged on a smartphone can be used to recreate context: to look up the weather at each moment,
% h - retrieve street side photos (for example, from Google Street View) at every step...transportation \cite{zheng2008learning} - suggested by Numair
retrieve street side photos (e.g. from Google Street View) at every step, and compute the mode of transportation (e.g., \cite{zheng2008learning}) and nearby geographical features. The Rewind system takes those cues and manipulates the conditions of retrieved photos to re-imagine what a person saw at some past point in time. The sequences of visuals are stitched together into an interface that allows users to directly manipulate the point in time being shown by scrubbing back and forth (Figure~\ref{fig:scrubbing}). So all a person has to do is enable location tracking on their mobile device to later rewind and re-experience a past trip.

@@

\section{Related Work}
% heather - trips vs locations -> (define) semantic memory vs episodic memory - check references, relate to some work done by SenseCam perhaps?
% cut down GPS usage
\subsection{Digital Memories}
Rewind is guided by literature about mediated memories, which provides a theoretical underpinning behind how the Rewind experience is constructed. \textit{Mediated Memories in the Digital Age} offers inspiration informing the relationship between experiences and memories \cite{van2007mediated}. van Dijck notes, ``Remembering is vital to our well being, because without autobiographical memories we would have no sense of past or future, and we would lack any sense of continuity'' (pg. 3). Rewind aims to give the user this sense of continuity in a time segment which has a past and future. By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner. Similarly in his seminal paper \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through``associative trails'', giving mankind the ability of``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''. Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one\’s sensory experiences about past visits.

@@

% heather - need to be rephrased perhaps? Should we give a high level summary of all the relationships we've found? More analysis to be done for photo vs. videos, another table?
% semantic vs episodic memory
% mention distance categories in the beginning (up up up) + everything else 
\section{Findings}
The findings of our user study center on the participants’ relationships to the Rewinds generated from their location data compared to the static photos. We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds. We also discuss the participants' interactions with and reactions to their Rewinds. The results use data from the user studies conducted with 12 men and 6 women. Half of the participants identified themselves as frequent travelers. Additionally, half of the participants were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them. We used Chi-squared one-tail test for significance analysis.

Our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media.
\begin{enumerate}
	\item Distance: how does the location's distance away from the participant's home influence the participant's perception of Rewinds and static photos? Distances ranged from 0 to 206,155 meters. For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 was 10--100 meters; Group 2 was 100--1,000 meters; Group 3 was 1,000--10,000 meters; Group 4 was 10,000--100,000 meters and Group 5 was 100,000--1,000,000 meters from the participant's home location.  
	\item Visit frequency: do participants react differently to Rewinds and static photos depicting locations they visit frequently compared to locations they rarely visit? We showed locations that were either ``most frequently visited,'' ``least frequently visited,'' or randomly selected.
	\item Companions: how does the presence of a traveling companion affect the participant's attitude toward Rewinds or static photos?
	\item Traveler type: do attitudes toward Rewinds and static photos differ depending on whether the participant identifies as a frequent traveler?
	\item GPS usage: do participants who are regular users of GPS navigation react differently to Rewinds and static photos compared to participants who don't use GPS navigation regularly?
\end{enumerate}
